Model-based variable selection for regression with highly correlated variables.

### 2014-05-27 www/article13.tex
up non lin
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@625 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\FloatBarrier
\subsubsection{non-linear case}

We have generated a non-linear structure to test the robustess of the model. $\boldsymbol{X}_f$ is a set of 6 independent Gaussian mixtures defined as previously but with random signs for the components means. $\boldsymbol{X}_r=\boldsymbol{X}_7=a\boldsymbol{X}_1^2+\boldsymbol{X}_2-2\boldsymbol{X}_3+ \varepsilon$. The matrix $\boldsymbol{X}$ is then scaled and we get $\boldsymbol{Y}=\sum_{i=1}^7\boldsymbol{X}_i+\varepsilon_Y$. We let $a$ vary between $0$ and $10$ to increase progressively the non-linear part of the sub-regression.

 \begin{figure}[h!] 
	\begin{minipage}[l]{.48\linewidth}
			\includegraphics[height=180px,width=245px]{figures/res_article/robust_S.png} 
			\caption{Frequency of true $\boldsymbol{X}_r$ found (plain)   when the paramater $a$ increases}\label{resnonlin}
	\end{minipage} \
   \begin{minipage}[r]{.48\linewidth}
			\includegraphics[height=180px,width=240px]{figures/res_article/robust_MSE.png} \label{MSEnonlin}
			\caption{MSE on the main regression for OLS(thick) and LASSO (thin) used both with (plain) or without CorReg (dotted).}
   \end{minipage}
\end{figure}
Figure \ref{MSEnonlin} illustrates the advantage of using CorReg even with non-linear structures. Figure \ref{resnonlin} shows that the MCMC have more difficulties to find a linear structure as the non-linear part of the sub-regression increases but the model is quite robust (efficient for small values of $a$)

>>>>

\FloatBarrier
\subsubsection{Non-linear case}

We have generated a non-linear structure to test the robustess of the model. $\boldsymbol{X}_f$ is a set of 6 independent Gaussian mixtures defined as previously but with random signs for the components means. $\boldsymbol{X}_r=\boldsymbol{X}_7=a\boldsymbol{X}_1^2+\boldsymbol{X}_2+\boldsymbol{X}_3+ \varepsilon$. The matrix $\boldsymbol{X}$ is then scaled and we get $\boldsymbol{Y}=\sum_{i=1}^7\boldsymbol{X}_i+\varepsilon_Y$. We let $a$ vary between $0$ and $10$ to increase progressively the non-linear part of the sub-regression.

 \begin{figure}[h!] 
	\begin{minipage}[l]{.48\linewidth}
			\includegraphics[height=180px,width=245px]{figures/res_article/robust_S.png} 
			\caption{Frequency of true $\boldsymbol{X}_r$ found (plain)   when the paramater $a$ increases}\label{resnonlin}
	\end{minipage} \
   \begin{minipage}[r]{.48\linewidth}
			\includegraphics[height=180px,width=240px]{figures/res_article/robust_MSE.png} 
			\caption{MSE on the main regression for OLS(thick) and LASSO (thin) used both with (plain) or without CorReg (dotted).}\label{MSEnonlin}
   \end{minipage}
\end{figure}
Figure \ref{MSEnonlin} illustrates the advantage of using CorReg even with non-linear structures. Figure \ref{resnonlin} shows that the MCMC have more difficulties to find a linear structure as the non-linear part of the sub-regression increases but the model is quite robust (efficient for small values of $a$)
